Draft

### 2017-08-25 Thesis/Draft.Rmd
Add Introduction

---
title: "Draft"
author: "Tim Radtke"
date: "5/28/2017"
header-includes:
   #- \documentclass[a4paper,twoside,english]{article}
   - \usepackage[retainorgcmds]{IEEEtrantools}
   - \usepackage{bm}
   - \usepackage{amsmath}
   - \usepackage{bbm}
   - \newtheorem{theorem}{Theorem}
   - \newtheorem{lemma}{Lemma}
   - \newcommand{\KL}{\,\text{KL}}
   - \newcommand{\der}{\,\text{d}}
   #- \usepackage[top=1.5cm, bottom=1.5cm, outer=5cm, inner=2cm, heightrounded, marginparwidth=2.5cm, marginparsep=2cm]{geometry}
   #- \usepackage{fontspec}
   #-   \setmainfont{Arial}
keep_tex: TRUE
output:
  pdf_document:
    number_sections: true
    keep_tex: true
    toc: true
    toc_depth: 3
    #latex_engine: xelatex
fontsize: 12pt
urlcolor: blue
---

@@

The *Thresholding Bandit Problem* described in Locatelli et al. (2016) can be considered a variant of a variant. It can be framed into the wider literature of *Pure Exploration* multi-armed bandit problems. In particular, it shares characteristics with the *Top-$m$* problem. This problem is concerned with finding the $m$ best arms as described by the means of their corresponding distributions. This in turn is similar to the *combinatorial bandit* problem, which also aims at finding the $m$ best arms. However, it is able to pull several arms at once: Think of an online shop that shows five recommended products on a product detail page. These five recommended products might each be represented by an arm, and we look for the products with the largest mean conversion rate. The thresholding bandit problem we discuss here, however, is concerned with pulling a single arm at a time. And so a more appropriate situation is that of a website presenting a banner. Again, think of an online shop trying to promote a certain category. The content team came up with a number of different designs for the banner, and it's not clear how many click-throughs they will gather.

@@

In any case, the problem boils down to the following. As standard in multi-armed bandit problems, we have $K$ arms $\mathcal{A} = \{1, \dots K\}$. We can pull arm $k$ at time $t$ to collect feedback in form of the random variable $X_{k,t}$ which is distributed according to the arm's distribution $\nu_k$. In general, we are concerned with estimating for each arm $i$ the mean $\mu_i$ of its distribution $\nu_i$. In contrast to most bandit problems, however, we do not directly compare arms with each other by comparing their means. That would for example be the case for pure exploration bandits, where it is necessary to compare the arms because one aims to find the best one relative to the others. In the case of the thresholding bandit, however, we compare each arm's mean $\mu_i$ individually against the threshold $\tau \in \mathbb{R}$ which is known and fixed before the experiment. One might compare this to a pure exploration bandit in which the mean of the best arm is known upfront. We will see later that this fact leads to advantages in the design of algorithms which are not as readily available in other bandit settings.

In Locatelli (2016), the arms' distributions are assumed to follow an $R$-sub-Gaussian distribution. Under this assumption, the authors are able to proof a general lower bound as well as an algorithm with a matching upper bound. Both hinge upon the *complexity* of a given problem. Since bandit problems can differ in the number of the arms $K$ and the means of each arm, some pose easier identification problems than others. Indeed, in the thresholding problem, the difficulty of the problem naturally depends on how close (the means of the) distributions are to the fixed threshold. Intuitively, the closer a mean $\mu_i$ is to the threshold $\tau$, the more difficult it will be to distinguish the two successfully based on samples from the distribution $\nu_i$. For the case of the sub-Gaussian distributions, a natural measure of this distance is given by simply $\Delta_i = |\tau - \mu_i| + \epsilon$, where $\epsilon$ defines a $2\epsilon$ interval around the threshold $\tau$ in which we allow ourselves to make a mistake at no cost.

If we extend this idea to the set of arms $i \in \{1,...,K\}$ of a given bandit problem, a natural measure of the overall diffulty of the problem, or the problem's complexity, might be given by $H = \sum_{i=1}^{K} \Delta_i^{-2}$. In particular, it shows that just adding additional arms leads to an increase in complexity (since we need to sample more of them), just as smaller $\Delta_i$ will increase the complexity as arms become harder to classify. (WHERE DOES THIS COMPLEXITY ORIGINALLY COME FROM?)

@@

Another characteristic uniquely identifying bandit problems is the regret measure that we aim to optimize. As explained during the introduction, multi-armed bandits traditionally optimize cumulative regret. The notion of regret considered in the thresholding bandit, however, is more akin to the simple regret in pure exploration bandits or the error probability in sequential hypothesis testing. Indeed, one can most easily describe the regret in the thresholding case as the probability of making a misclassification of any arm. Or, more rigorously, let us define the set of all arms with mean larger than the threshold, $\mathcal{S}_\tau = \{i \in \mathcal{A}: \mu_i \geq \tau\}$. Consequently, $\mathcal{S}_\tau^C = \{i \in \mathcal{A}: \mu_i < \tau\}$. At the end of the sampling rule/procedure (!!we have not mentioned yet the fact that we're in the fixed budget case!!), we demand that any algorithm returns the two corresponding *estimated* sets: $\hat{\mathcal{S}}_{\tau} = \{i \in \mathcal{A}: \hat{\mu}_i \geq \tau\}$, as well as $\hat{\mathcal{S}}_{\tau}^C = \{i \in \mathcal{A}: \hat{\mu}_i < \tau\}$. We simply demand an answer to the question which arms have means above the threshold $/tau$, and which arms lie below  $\tau$. Let $T$ be the overall number of samples the algorithm is allowed to pull. We define the loss as $\mathcal{L}(T) = \mathbbm{1}_{\{\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset\}} \cdot \mathbbm{1}_{\{\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset\}}$. That is, we compare the return set with the true set and collect a loss of 1 if any arm with a true mean outside the $2\epsilon$ interval around $\tau$ was misclassified. It is important to realize that arms with means inside the $2 \epsilon$ interval may be misclassified without it affecting the loss. These arms are considered close enough to the threshold that we do not care whether they lie above or below.

@@

From there, it is natural to define the expected regret/loss as $\mathbb{E}[\mathcal{L}(T)] = \mathbb{P}((\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset) \land (\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset))$. This, of course, is the mentioned probability of making a mistake.

ADD REMARK ON WHAT THIS IMPLIES WITH REGARD TO THE MEANS

@@

At this point, we have defined the fixed budget thresholding bandit setup for any algorithm in the case of sub-Gaussian distributions. We thus proceed to describe the algorithm proposed in Locatelli et al. (2016).

@@

@@

From the general setup, we already know how the algorithm will end. After it has drawn $T$ samples, the algorithm makes its decision of which arms to include in the return sets solely on basis of the empirical means $\hat{\mu}_i(T)$ estimated based on the samples drawn until time $T$. Furthermore, the threshold and interval around the threshold were fixed upfront and serve as argument to the algorithm: $(\tau, \epsilon)$. For a given arm $i$ and a given time $t$, we let $T_i(t)$ represent the number of samples drawn from arm $i$ until time $t$ (including). Consequently, the empirical mean of arm $i$ at time $t$ is given by $\mu_i = \frac{1}{T_i(t)} \sum_{s=1}^{T_i(t)} X_{i,s}$ where $X_{i,s}$ is the feedback sampled from distribution $\nu_i$ when the arm is pulled for the $s$-th time.

@@

**Remark**: Obviously, the APT algorithm tends to pull arms more often with corresponding mean close to the threshold and interval (small $\hat{\Delta}_i(t))$. This makes sure that more evidence is gathered on arms which appear to be inherently difficult to classify based on the samples collected until time $T_i(t)$, as these arms stifle the confidence the most. That is, until we have collected enough evidence to make a confident classification even if the mean is truly close to the threshold. In that case, $\sqrt{T_i(t)}$ will raise $B_i(t+1)$. Consequently, other arms farther away from the threshold will be sampled again. In this way, the algorithm tries to distribute the budget $T$ over all arms so as to define a sampling rule optimizing the confidence of the final decision. This is Glivenko-Cantelli and the CLT making sure $B_i(t+1)$ is not degenerate. (?)

@@

Yet another idea, again mentioned in Locatelli et al. (2016) is to show bounds based on the Kullback-Leibler divergence of the specific distribution directly. While the approximation through the Gaussian Kullback-Leibler divergence in the lower bound proof is convenient and leads to the simple APT algorithm, it might not stay appropriate for distributions whose Kullback-Leibler divergence tends to differ from the Gaussian. This, for example, is the case for Bernoulli distributions at very small parameters $\mu$. By looking at the graphical examples below it becomes obvious that the Kullback-Leibler divergence of Bernoullis starts to lose any similarity to the plain quadratic approximation. The second graph then shows that the actual Kullback-Leibler divergence of Bernoullis also has lost any symmetry over this range of parameter values. Given that Bernoulli distributions with very small parameter values arise naturally in many applications in website optimization and advertising click-through modeling, there is a need to tackle this problem.

Refer also to page 6 in Kaufmann et al. (2016): "This information-theoretic lower bound permits to interpret the quantity $H(\nu)$ defined in (2) as a subgaussian approximation".

And so a potential approach can be to use the Kullback-Leibler divergence as measure similar to the methods proposed in Kaufmann et al. (2015). They proposed Kullback-Leibler based approaches for the pure exploration bandit setting, which we will describe in chapter 2. Then, in chapter 3, we will come back to the problem of using the Kullback-Leibler divergence in the thresholding bandit setting.

@@

## Upper Bound: Theorem and Proof

@@

*Proof of Theorem \ref{theorem:LocatelliTheorem4}:* To prove above theorem, we first define a favorable event $\xi$ on which we hope
to make a loss with only a small probability. Indeed, it is the event for which
we want to upper bound the expected loss. As we want to find an upper bound for
the expected loss of the APT algorithm, the event corresponds to the decision
made by it. Given that the APT algorithm's sampling rule and final decision is based on the empirical mean of each arm, it will have low expected regret, if it finds empirical mean estimates $\hat{\mu}_i(t) = \frac{1}{s} \sum_{t=1}^s X_{i,t}$
that are close to the true means $\mu_i$ of the arms. Then, we would
expect arms with $\hat{\mu}_i(T) > \tau + \epsilon$ to be classified correctly, and
arms with $\hat{\mu}_i(T) < \tau - \epsilon$ to be rejected.

Indeed, we have $\mathbb{E}(\mathcal{L}(T)) = P(S_{\tau + \epsilon} \cap
\hat{S}_\tau^C \neq \emptyset \lor S_{\tau-\epsilon}^C \cap \hat{S}_{\tau} \neq
\emptyset)$. But this just corresponds to $P(\{\exists i: ((\mu_i <
\tau-\epsilon) \land(\hat{\mu}_i \geq \tau)) \lor ((\mu_i > \tau + \epsilon)
\land (\hat{\mu}_i < \tau)))$. Each of the two $(...)\lor(...)$ conditions
corresponds to $| \hat{\mu}_i - \mu_i | \geq \epsilon$. It follows that the
expected loss can be rewritten as: $\mathbb{E}(\mathcal{L}(T)) = P(\exists i,
\exists s: |\hat{\mu}_{i,s} - \mu_i | \geq \epsilon) = P(\xi^C)$. This is
exactly the probability of classifying at least one arm incorrectly which
results in a loss of size 1.

Thus we define as the favorable event as:

\begin{equation} 
\xi = \{\forall i, \forall s: | \hat{\mu}_{i,s} - \mu_i | \leq
\epsilon\} 
\end{equation}

Furthermore, if we write $\xi_{i,s} = \{ |\hat{\mu}_{i,s}-\mu_i | \leq \epsilon
\}$, then the following holds by a union bound.

\begin{equation} 
P(\xi) = P(\cap_i \cap_s \xi_{i,s}) = 1 - P(\cup_i \cup_s
\xi_{i,s}^C) \geq 1 - \sum_i \sum_s P(| \hat{\mu}_{i,s} - \mu_i| \geq \epsilon)
\label{theorem2_prob_fav_event} 
\end{equation}

Furthermore, for any $i \in \{1, \dots, K\}$, for any $s \in \{1, \dots,
T(i)\}$, with $X_{it}$ being the random sample from the R-sub-Gaussian
distribution $v_i$ at time $t$:

\begin{equation} 
P(| \hat{\mu}_{i,s} - \mu_i| \geq \epsilon) = P(| (\frac{1}{s}
\sum_{t=1}^{s} X_{it} - \mu_i) | \geq \epsilon) = P(| \sum_{t=1}^{s} (X_{it} -
\mu_i) | \geq s \epsilon) 
\end{equation}

where the latter can be bounded by a Hoeffding inequality:

\begin{equation} 
P(| \sum_{t=1}^{s} (X_{it} - \mu_i) | \geq s \epsilon) \leq
2\exp (-\frac{\epsilon^2 s}{2 R^2}) \label{theorem2_hoeffding} 
\end{equation}

The Hoeffding inequality as used here is as follows (compare chapter 2.4 in [David Pollard (2015)](http://www.stat.yale.edu/~pollard/Books/Mini/Basic.pdf)):

\begin{lemma}[Hoeffding's Inequality] \label{lemma:HoeffdingInequality}
Consider $X_1, \dots, X_T$ independent random variables from R-sub-Gaussian distributions $\nu_i$ with mean $\mu_i$. Then, for any $\epsilon > 0$,

>>>>

---
title: "Draft"
author: "Tim Radtke"
date: "5/28/2017"
header-includes:
   #- \documentclass[a4paper,twoside,english]{article}
   - \usepackage[retainorgcmds]{IEEEtrantools}
   - \usepackage{bm}
   - \usepackage{amsmath}
   - \usepackage{bbm}
   - \usepackage[lined,boxed]{algorithm2e}
   - \newtheorem{theorem}{Theorem}
   - \newtheorem{lemma}{Lemma}
   - \newcommand{\KL}{\,\text{KL}}
   - \newcommand{\der}{\,\text{d}}
   #- \usepackage[top=1.5cm, bottom=1.5cm, outer=5cm, inner=2cm, heightrounded, marginparwidth=2.5cm, marginparsep=2cm]{geometry}
   #- \usepackage{fontspec}
   #-   \setmainfont{Arial}
keep_tex: TRUE
output:
  pdf_document:
    number_sections: true
    keep_tex: true
    toc: true
    toc_depth: 2
    #latex_engine: xelatex
fontsize: 12pt
urlcolor: blue
---

"In general, we look for a new law by the following process: First we guess it. Then we – now don't laugh, that's really true. Then we compute the consequences of the guess to see what, if this is right, if this law that we guessed is right, to see what it would imply. And then we compare the computation results to nature, or we say compare to experiment or experience, compare it directly with observations to see if it works. If it disagrees with experiment, it's wrong. In that simple statement is the key to science. It doesn't make any difference how beautiful your guess is, it doesn't make any difference how smart you are, who made the guess, or what his name is. If it disagrees with experiment, it's wrong. That's all there is to it."

- Richard Feynman in *Richard Feynman Messenger Lectures at Cornell University: The Character of Physical Law. Chapter 7, Seeking New Laws*.

# Abbreviations

Kullback-Leibler divergence between distributions $\nu_i$ and $\nu_j$: $\KL(\nu_i||\nu_j)$.

Binary relative entropy: $d(x,y) := x \log(x/y) + (1-x) \log((1-x)/(1-y))$, where $d(0,0) = d(1,1) = 0$.

Kullback-Leibler divergence for two Bernoulli distributions parameterized by their means $\mu_i$ and $\mu_j$: $KL_{Ber}(\nu_i||\nu_j) = d(\mu_i, \mu_j)$.

# Introduction to Sequential Sampling and Multi-Armed Bandits

The thesis at hand joins the ranks of a large literature concerned with the general problem of sequential sampling. One is familiar with the idea of "batch sampling", where the entire sample is gathered first and analyzed only after the last sample has become available. However, as noted in Chernoff (1958), many situations arise in which one would like to gather feedback from samples as they are drawn so as to influence the choice of the next sample. The two fundamental characteristics of the latter sampling process are that it is sequential and adaptive. Since observations are drawn in sequence, one has a chance to observe the observations drawn so far in order to adapt the decision of what sample one would like to observe next.

This makes sequential sampling especially relevant in situations where there is a inherent cost to drawing an observation. The classical example that of clinical trials in which a researcher tests two drugs on patients to observe which one performs better. Not only is it difficult to gather patients, but also one would like to adapt the sampling such that as soon as possible more patients receive the better drug so that more patients are cured. As noted in Cappé et al. (2013), this example dates back to Thompson (1933, 1935). Such problems are known as multi-armed bandit problems in which the sampling is adapted so as to minimize the cumulative regret: In the case of the drug tests, one would like to sample the two drugs in a way to find the best drug as soon as possible and then to test this drug more and more often and more often than the worse drug. This would lead to cumulatively more healthy patients then when both drugs are tested uniformly and thus minimize the regret from treating a patient with an ineffective drug.

Instead of drugs, can consider two or more unknown distributions (which we call arms in the multi-armed bandit problem). These distributions have different means, and one can draw samples sequentially from the distributions in order to estimate their means. One would like to play the distribution with the highest mean to minimize the cumulative regret measure. How can we organize the sampling in order to achieve this goal?

While Gittins (1979) presents an Bayesian-optimal solution, the Upper-Confidence Bound algorithms pioneered by Agrawal (1995) and Auer, Cesa-Bianchi and Fischer (2002) lead to a blooming literature on multi-armed bandit problems that has been picked up to solve modern problems in website and advertising optimization, where advertisers try to allocate their advertising optimally so as to reduce regret from showing poorly converting advertisements. Several algorithms as the KL-UCB algorithm based on Kullback-Leibler divergence upper confidence intervals (Cappé et al., 2013) or the Bayes-UCB algorithm (Kaufmann et al., 2012)  have followed and been shown to be optimal as they reach the lower bound introduced in Lai and Robbins (1985) and Burnetas and Katehakis (1996).

These algorithms have in common that they compute after any sample an index for each of the unknown distributions. This index is based solely on the past (observed) data, and then used to pick the distribution from which the next observation should be drawn. Using these indexes, the algorithms can sequentially sample and adapt the future strategies to observations as they are gathered.

Other algorithms based on indices can be used on related problems. Instead of minimizing cumulative regret, it might be more interesting to find the best arm, that is, the distribution with the largest mean, with as few samples as possible and with confidence as large as possible. This is particularly useful when there is not necessarily a cost from initially picking a lower mean, but when drawing any sample is costly, and one needs to explore the distributions as efficiently as possible. The need for strategies other than uniform sampling arises: Do not continue to sample distributions that we are confident about. As such, the best arm identification problem is very similar to the problem faced in Bayesian Optimization: Training large neural networks is costly in terms of time and computation, and so the parameter space needs to be explored with as few samples as possible. (Zhang et al., 2017; Brochu et al., 2010).

The problem of best arm identification is very related to statistical hypothesis testing as noted by Chernoff (1958) since in the end, one has to make a decision about how the means of distributions relate to each other. The main difference of course being that the sampling procedure becomes integrated into the evaluation of the distributions. Given the focus on exploration, the problem is usually described with a loss function different from cumulative regret. Audibert et al. (2010) introduce a soft measure called *simple regret* based on which they describe UCB policies. Other authors investigate hard, binary measures that are equal to 1 when the best arm has not been identified (Russo, 2016; Garivier and Kaufmann, 2016). These binary measures correspond to the probability of the identified arm being the best, and thus inherently related to hypothesis testing. The problem of best arm identification can readily be extended to the so called Top-$m$ problem of identifying the best $m$ of $K$ arms (Kaufmann and Kalyanakrishnan, 2013; Kaufmann et al. 2016).

In this thesis, we consider the thresholding bandit problem. Instead of identifying the best $m$ out of $K$ arms, one aims to find all out of $K$ distributions that have a mean larger than a threshold fixed upfront. In the form described in Locatelli et al. (2016), algorithms in the thresholding bandit problem are evaluated against a binary loss function penalizing whenever an arm has not been classified correctly as being above the threshold and thus focus on exploration similar to algorithms employed for best arm identification. Indeed, Locatelli et al. (2016) show how their thresholding algorithm can be used for best arm identification when the mean of the best arm is known upfront.

In the following, we first present the thresholding bandit problem in detail. To then extend upon the algorithm proposed by Locatelli et al. (2016), we first explore how the Kullback-Leibler divergence has been employed in the best arm identification literature by Garivier and Kaufmann (2016) and Kaufmann et al. (2016). We shortly describe two variance based algorithms for the thresholding bandit problem introduced in Mukherjee et al. (2017) and Zhang et al. (2017), before introducing the new Simple Likelihood Ratio algorithm. We end with experiments to examine the performance of different algorithms.

@@

The *Thresholding Bandit Problem* described in Locatelli et al. (2016) can be considered a variant of a variant. It can be framed inside of the wider literature of *Pure Exploration* multi-armed bandit problems. In particular, it shares characteristics with the *Top-$m$* problem. This problem is concerned with finding the $m$ best arms as described by the means of their corresponding distributions. This in turn is similar to the *combinatorial bandit* problem, which also aims at finding the $m$ best arms. However, it is able to pull several arms at once: Think of an online shop that shows five recommended products on a product detail page. These five recommended products might each be represented by an arm, and we look for the products with the largest mean conversion rate. The thresholding bandit problem we discuss here, however, is concerned with pulling a single arm at a time. And so a more appropriate situation is that of a website presenting a banner. Again, think of an online shop trying to promote a certain category. The content team came up with a number of different designs for the banner, and it's not clear how many click-throughs they will gather.

@@

In any case, the problem boils down to the following. As usual in multi-armed bandit problems, we have $K$ arms $\mathcal{A} = \{1, \dots K\}$. We can pull arm $k$ at time $t$ to collect feedback in form of the random variable $X_{k,t}$ which is distributed according to the arm's distribution $\nu_k$. In general, we are concerned with estimating for each arm $i$ the mean $\mu_i$ of its distribution $\nu_i$. In contrast to most bandit problems, however, we do not directly compare arms with each other by comparing their means. That would for example be the case for pure exploration bandits, where it is necessary to compare the arms because one aims to find the best one relative to the others. In the case of the thresholding bandit, however, we compare each arm's mean $\mu_i$ individually against the threshold $\tau \in \mathbb{R}$ which is known and fixed before the experiment. One might compare this to a pure exploration bandit in which the mean of the best arm is known upfront. We will see later that this fact leads to advantages in the design of algorithms which are not as readily available in other bandit settings.

In Locatelli (2016), the arms' distributions are assumed to follow an $R$-sub-Gaussian distribution. Under this assumption, the authors are able to proof a general lower bound as well as an algorithm with a matching upper bound. Both hinge upon the *complexity* of a given problem. Since bandit problems can differ in the number of the arms $K$ and the means of each arm, some pose easier identification problems than others. Indeed, in the thresholding problem, the difficulty of the problem naturally depends on how close (the means of the) distributions are to the fixed threshold. Intuitively, the closer a mean $\mu_i$ is to the threshold $\tau$, the more difficult it is to distinguish the two successfully based on samples from the distribution $\nu_i$. A straightforward measure of this distance is given by $\Delta_i = |\tau - \mu_i| + \epsilon$, where $\epsilon$ defines a $2\epsilon$ interval around the threshold $\tau$ in which we allow ourselves to make a mistake at no cost. In the case of sub-Gaussian distributions, this distance is not only simple but can be interpreted very naturally as we will come to understand later.

If we extend this idea to the set of arms $i \in \{1,...,K\}$ in a given bandit problem, a measure of the overall diffulty of the problem, or the problem's complexity, might be given by $H = \sum_{i=1}^{K} \Delta_i^{-2}$. In particular, it shows that just adding additional arms leads to an increase in complexity (since we need a larger budget to sample each arm the same number of times as before). Likewise, a smaller $\Delta_i$ increases the complexity as arms become harder to classify. Choosing the complexity measure in this way fits the distance measure $\Delta_i$ and turn out to be useful in the proof of an upper bound for the APT algorithm presented in Locatelli et al. (2016).

@@

Another characteristic uniquely identifying bandit problems is the regret measure that we aim to optimize. As explained during the introduction, multi-armed bandits traditionally optimize cumulative regret. The notion of regret considered in the thresholding bandit, however, is more akin to the simple regret in pure exploration bandits or the error probability in sequential hypothesis testing. Indeed, one can most easily describe the regret in the thresholding case as the probability of misclassifying any arm. Or, more rigorously, define the set of all arms with mean larger than the threshold, $\mathcal{S}_\tau = \{i \in \mathcal{A}: \mu_i \geq \tau\}$. Consequently, $\mathcal{S}_\tau^C = \{i \in \mathcal{A}: \mu_i < \tau\}$. At the end of the sampling rule/procedure (!!we have not mentioned yet the fact that we're in the fixed budget case!!), we demand that any algorithm returns the two corresponding *estimated* sets: $\hat{\mathcal{S}}_{\tau} = \{i \in \mathcal{A}: \hat{\mu}_i \geq \tau\}$, as well as $\hat{\mathcal{S}}_{\tau}^C = \{i \in \mathcal{A}: \hat{\mu}_i < \tau\}$. We simply demand an answer to the question which arms have means above the threshold $/tau$, and which arms lie below  $\tau$. Let $T$ be the overall number of samples the algorithm is allowed to pull. We define the loss as $\mathcal{L}(T) = \mathbbm{1}_{\{\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset\}} \cdot \mathbbm{1}_{\{\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset\}}$. That is, we compare the return set with the true set and collect a loss of 1 if any arm with a true mean outside the $2\epsilon$ interval around $\tau$ was misclassified. It is important to realize that arms with means inside the $2 \epsilon$ interval may be misclassified without it affecting the loss. These arms are considered close enough to the threshold that we do not care whether they lie above or below.

@@

Now, the expected regret/loss is defined as $\mathbb{E}[\mathcal{L}(T)] = \mathbb{P}((\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset) \land (\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset))$. This, of course, is the mentioned probability of making a mistake.

@@

At this point, we have defined the fixed budget thresholding bandit setup for any algorithm in the case of sub-Gaussian distributions. We thus proceed to describe the APT algorithm proposed in Locatelli et al. (2016).

@@

\IncMargin{1em}
\begin{algorithm}
\SetKwData{Left}{left}\SetKwData{This}{this}\SetKwData{Up}{up}
\SetKwFunction{Union}{Union}\SetKwFunction{FindCompress}{FindCompress}
\SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
\Input{$\tau$, $\epsilon$}
\Output{$\hat{S}_{\tau} = \{k: \hat{\mu}_k(T) \geq \tau\}$}
\BlankLine
\emph{Pull each arm once}\;
\For{$t = K+1$ \KwTo $T$}{
  \emph{Pull arm $I_t = \arg \min_{k\leq K} B_k^{APT}(t) = \sqrt{T_k(t)} \sqrt{|\hat{\mu}_i(t) - \tau|+\epsilon}$}\;
  \emph{Observe reward $X \sim \nu_{I_t}$}\;
}
\caption{Anytime Parameter-free Thresholding Algorithm (Locatelli et al., 2016)}\label{algo_apt}
\end{algorithm}\DecMargin{1em}

@@

From the general setup, we already know how the algorithm will end. After it has drawn $T$ samples, the algorithm makes a decision of which arms to include in the return sets on basis of the empirical means $\hat{\mu}_i(T)$ estimated based on the samples drawn until time $T$. Furthermore, the threshold and interval around the threshold are fixed upfront and serve as argument to the algorithm: $(\tau, \epsilon)$. For a given arm $i$ and a given time $t$, we let $T_i(t)$ represent the number of samples drawn from arm $i$ until time $t$ (including). Consequently, the empirical mean of arm $i$ at time $t$ is given by $\hat{\mu}_i(t) = \frac{1}{T_i(t)} \sum_{s=1}^{T_i(t)} X_{i,s}$ where $X_{i,s}$ is the feedback sampled from distribution $\nu_i$ when the arm is pulled for the $s$-th time.

@@

**Remark**: Obviously, the APT algorithm tends to pull arms more often with corresponding mean close to the threshold and interval (small $\hat{\Delta}_i(t))$. This makes sure that more evidence is gathered on arms which appear to be inherently difficult to classify based on the samples collected until time $T_i(t)$, as these arms stifle the confidence the most. That is, until we have collected enough evidence to make a confident classification even if the mean is truly close to the threshold. In that case, $\sqrt{T_i(t)}$ will raise $B_i(t+1)$. Consequently, other arms farther away from the threshold will be sampled again. In this way, the algorithm tries to distribute the budget $T$ over all arms so as to define a sampling rule optimizing the confidence of the final decision.

@@

Yet another idea, again mentioned in Locatelli et al. (2016) is to show bounds based on the Kullback-Leibler divergence of the specific distribution directly. While the approximation through the Gaussian Kullback-Leibler divergence in the lower bound proof is convenient and leads to the simple APT algorithm, it might not stay appropriate for distributions whose Kullback-Leibler divergence tends to differ from the Gaussian. This, for example, is the case for Bernoulli distributions at very small parameters $\mu$. By looking at the graphical examples below it becomes obvious that the Kullback-Leibler divergence between Bernoulli distributions starts to lose any similarity to the quadratic approximation. The second graph then shows that the actual Kullback-Leibler divergence of Bernoulli distributions loses any symmetry over this range of parameter values. Given that Bernoulli distributions with very small parameter values arise naturally in many applications in website optimization, advertising click-through modeling, or anomaly detection in time series, there is a need to tackle this problem.

Refer also to page 6 in Kaufmann et al. (2016): "This information-theoretic lower bound permits to interpret the quantity $H(\nu)$ defined in (2) as a subgaussian approximation". In the case of Normal distributions with known and equal mean, it holds that the Kullback-Leibler divergence between $\nu_i$ and $\nu_j$, parameterized by $\mu_i$ and $\mu_j$, can be written as

$$
\KL_{Normal}(\nu_i || \nu_j) = 2(\mu_i - \mu_j)^2.
$$

Writing $\mu_j = \tau$ and $\epsilon = 0$, we see that the APT algorithm essentially measures the KL-divergence between two Normal distributions. For two Bernoulli distributions $\nu_i$ and $\nu_j$, parameterized by $\mu_i$ and $\mu_j=\tau$, we write

$$
\KL_{Ber}(\nu_i||\nu_j) = \mu_i \log(\frac{\mu_i}{\tau}) + (1-\mu_i) \log(\frac{1-\mu_i}{1-\tau})
$$

In the case of $\tau = 0.5$, the latter KL-divergence is symmetric in its first argument, and thus can be well approximated by Pinsker's inequality:

$$
\KL_{Ber}(\nu_i||\nu_j) \geq 2(\mu_i - \tau)^2.
$$

This shows how the distance measure used in the APT algorithm, and consequently the complexity $H$, is a useful approximation of the KL-divergence for sub-Gaussian distributions. However, this approximation suffers as the distributions less and less similar to Gaussian distributions. Thus similarly to how UCB algorithms in the cumulative regret setting have been extended to KL-UCB algorithms (compare Cappé et al., 2013), also the APT algorithm offers room for improvement.

And so a potential approach can be to use the Kullback-Leibler divergence as measure similar to the methods proposed in Kaufmann et al. (2015). They proposed Kullback-Leibler based approaches for the pure exploration bandit setting, which we will describe in chapter 2. Then, in chapter 3, we will come back to the problem of using the Kullback-Leibler divergence in the thresholding bandit setting. To conclude chapter 1, we proof the lower bound and upper bound for the APT algorithm as presented Theorem 1 and Theorem 2 in Locatelli et al. (2016).

@@

## Upper Bound on Expected Loss of APT

@@

*Proof of Theorem \ref{theorem:LocatelliTheorem4}:*

In order to upper bound the expected loss of the APT algorithm, we want to find an event on which the algorithm would correctly seperate arms from the threshold, that is, on the event a seperation condition holds. We then want to show that with large probability, this *favorable* event does indeed hold. Consequently, the expected loss (probability of an error) will correspond to the probability that the favorable event does not hold after all as this leads the seperation condition to fail, and the algorithm to classify at least one arm incorrectly.

While this is the general idea, we have to jump between seperation condition, favorable event, and large probability.

### Separation Condition

As noted in Zhong et al. (2017), a simple requirement to correctly classify arms at the final round is the following. For every arm $i \in \{1, ..., K\}$ at round $T$,

$$
\hat{\mu}_{i,T_i(n)} \geq \mu_i - \frac{\mu_i - \tau + \epsilon}{2} \quad \text{if} \quad \mu_i \geq \tau
$$
or

$$
\hat{\mu}_{i,T_i(n)} \leq \mu_i + \frac{\tau - \mu_i + \epsilon}{2} \quad \text{if} \quad \mu_i < \tau
$$
Or simply in terms of the gap between the arm and the threshold as used as index by the algorithm,

$$
| \hat{\mu}_{i, T_i(n)} - \mu_i | \leq \frac{|\mu_i - \tau| + \epsilon}{2} = \frac{\Delta_i}{2}.
$$

Intuitively, the conditions make sense as they ensure that the current mean estimate is closer to the true mean than to the threshold. Consequently, there is no possible arrangement left in which the condition would hold, but the arm be classified incorrectly. Assuming $\mu_i < \tau$ and $\epsilon = 0$, an incorrect classification would require $\mu_i < \tau \leq \hat{\mu_i}$. But then  $| \hat{\mu}_{i, T_i(n)} - \mu_i | \geq |\mu_i - \tau|$, violating the separation condition.

Thus, we need to show that in the very final round, this condition holds for every arm $i \in \{1,...,K\}$ with large probability. Or more precisely, we need to derive a bound on the probability with which this does not hold.

### The Favorable Event

The separation condition gives a good idea of what event we need to hold in order to make a correct classification. The smaller the deviation of the empirical mean from the population mean, the more difficult it is for the classification to be wrong. Moreover, if the mean and empirical mean are identical, then the classification is correct independent of the threshold. And furthermore, the closer the mean and the threshold are, the better the estimate must be for a correct classification.

Having to bound the absolute deviation of the sample mean from the population mean is a very thankful operation. Define the favorable event $\xi$ as

$$
\xi = \Big\{\forall i \in \mathbb{A}, \forall s \in \{1,...,T\} : |\frac{1}{s} \sum_{t=1}^{s}X_{i,t} - \mu_i| \leq \sqrt{\frac{T \delta^2}{H s}} \Big\}.
$$

We want the probability that this favorable event occurs to be large, that is, the probability that the deviation is small, such that the separation condition holds with large probability. Indeed, we bound the deviation for *all* arms $i \leq K$ and for *every* round $s \leq T$. Using some Chernoff Hoeffding bounds, we are able to write

$$
\mathbb{P}(\xi) \geq 1 - 2(\log(T) +1)K \exp(-\frac{T\delta^2}{2R^2H})
$$

### Need to Bound $T_i$

We now have that with large probability, the favorable event holds. On the favorable event, we have for every arm $i$:

$$
| \hat{\mu}_i(t) - \mu_i| \leq \sqrt{\frac{T\delta^2}{HT_i(t)}}
$$
